From Causal Discovery to Intervention Simulation: Modeling Precariousness and Depression in the HELIUS Study

### 2025-06-28 draft_v1/draft_v2.qmd
update draft

* $S$ is a fixed or exogenous input (external financial stress),
* $\alpha_{DP}$ represents the feedback from precariousness to depression,
* $\alpha_{PD}$ represents the feedback from depression to precariousness,
* $\alpha_{DS}$ and $alpha_{PS}$ capture the direct effects of $S$,
* $\sigma_D, \sigma_P$ are stochastic noise amplitudes,
* $\eta_D(t), \eta_P(t)$ are independent standard Wiener processes.

>>>>

* $S$ is a fixed or exogenous input (external financial stress),
* $\alpha_{DP}$ represents the feedback from precariousness to depression,
* $\alpha_{PD}$ represents the feedback from depression to precariousness,
* $\alpha_{DS}$ and $\alpha_{PS}$ capture the direct effects of $S$,
* $\sigma_D, \sigma_P$ are stochastic noise amplitudes,
* $\eta_D(t), \eta_P(t)$ are independent standard Wiener processes.
